### 2016-06-21 Paper_v1.tex
June 20th by CHS.
June 21st by Shih

@@

\end{document}

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_bounded.pdf}
\caption{Total-order global sensitivities for limiting all controllable initial conditions}
\label{fig:AAs_bounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_unbounded.pdf}
\caption{Total-order global sensitivities for each amino acids in the case that each of them are unbounded respectively.}
\label{fig:AAs_unbounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/C_Secretion.pdf}
\caption{Global sensitivity analysis for alternative carbon sources while glutamic acid as the indication of amino acids.}
\label{fig:C_Secretion.pdf.pdf}
\end{figure}

@@

\end{document}
\grid
